---
title: "da-ws-01-1"
author: "keltoskytoi"
date: "23 Oktober 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## **R Markdown Learning log entry**

***My favourite aspect*** is that this is the way I can start to understand how programming languages work including linux (ubuntu) and others. Being more of a social scentist and not a natural scientist it is had to get an entry which fits to our purposes. 

***Eureka effect*** so far: wow, this is what I want to learn. So far it is very logical and smoother to handle than I thought. I hope I´ll stay to this comment even after several weeks! 

***Questions***: I have too many

```{r}
a <- 2
b <- 5 
r1 <- a + b
r2 <- a - b
r3 <- a * b
r4 <- a / b
v1 <- c(r1,r2,r3,r4)
v1 <- c(r1,r2,r3,r4,a**b)
print(v1)
v2 <- c("sum", "difference", "product", "ratio", "power")
print(v2)
df <- data.frame (SPALTE1 = v1, SPALTE2 = v2)
colnames(df, do.NULL = FALSE)
colnames(df) <- c("Results","Operation")
print(df)
print(df[3,1])
```


