---
title: "da-ws-06-02_b"
author: "keltoskytoi, Jana Schönemann, Sebastian Richter"
date: "28 November 2016"
output: html_document
---

```{r}
path_main <- "C:/Users/Keltoskytoi/Desktop/"
path_data <- paste0(path_main, "data/")
path_input <- paste0(path_data, "data_analysis/input/")
path_output <- paste0(path_data, "data_analysis/output/")
path_temp <- paste0(path_data, "data_analysis/temp/")
path_csv <- paste0(path_data, "data_analysis/csv/")
path_fun <- paste0(path_data, "data_analysis/fun/")

library(car)
library(lmtest)
```
# Organising the data
```{r }
df <- read.table(paste0(path_csv, "115-46-4_feldfruechte.txt"),
                 skip = 6, header = TRUE, sep = ";", dec = ",", fill = TRUE, 
                 encoding = "ANSI")

df <- df[1:8925,]

names(df) <-c("Year", "ID", "Place", "Winterweizen", "Roggen+Wintermenggetreide",  "Wintergerste",  "Sommergerste", "Hafer", "Triticale", "Kartoffeln", "Zuckerrüben", "Winterraps", "Silomais")

for (c in colnames(df) [4:13]){
  df[, c] [df[, c]== "."] <-NA
  df[, c] [df[, c]== "0,0"] <-NA
  df[, c] <- as.numeric(sub(",",".",as.character(df[, c])))
}

```
# Relation between Wintergerste and Winterweizen

```{r }
ind<-df$Wintergerste
dep<-df$Winterweizen
plot(dep, ind)
abline(lmod, col = "green")
```
# Preparations for the "leave many out cross validation" 
```{r }
nrow(df)
head(df)
df <- df[!is.na(df$Wintergerste), ]
df <- df[!is.na(df$Winterweizen), ]
remaining <- c("Wintergerste", "Winterweizen")
df_new <- df[, remaining]
head(df_new)
summary(df_new)

range <- nrow(df)
nbr <- nrow(df) * 0.8
```
# Leave many out cross validation
```{r }
cv <- lapply(seq(100), function(i){
  set.seed(i)
  smpl <- sample (range, nbr)
  train <- df_new[smpl, ]
  test <- df_new[-smpl, ]
  lmod <- lm(Winterweizen ~ Wintergerste, data=train)
  pred <- predict(lmod , newdata = test)
  obsv <- test$Winterweizen
  resid <- obsv-pred   
  ss_obsrv <- sum((obsv - mean(obsv))**2)
  ss_model <- sum((pred - mean(obsv))**2)
  ss_resid <- sum((obsv - pred)**2)
  mss_obsrv <- ss_obsrv / (length(obsv) - 1)
  mss_model <- ss_model / 1
  mss_resid <- ss_resid / (length(obsv) - 2)
  data.frame(pred = pred,
             obsv = obsv,
             resid = resid,
             ss_obsrv = ss_obsrv,
             ss_model = ss_model,
             ss_resid = ss_resid,
             mss_obsrv = mss_obsrv,
             mss_model = mss_model,
             mss_resid = mss_resid,
             r_squared = ss_model / ss_obsrv
  )             
})
cv <- do.call("rbind", cv)
summary(cv)

ss_obsrv <- sum((cv$obsv - mean(cv$obsv))**2)
ss_model <- sum((cv$pred - mean(cv$obsv))**2)
ss_resid <- sum((cv$obsv - cv$pred)**2)

mss_obsrv <- ss_obsrv / (length(cv$obsv) - 1)
mss_model <- ss_model / 1
mss_resid <- ss_resid / (length(cv$obsv) - 2)

plot(cv$obsv, (cv$obsv - cv$pred))
```
# Organising the results in a dataframe

```{r }
data.frame(NAME = c("cross-validation F value",
                    "linear model F value", 
                    "cross-validatino r squared",
                    "linear model r squared"),
           VALUE = c(round(mss_model / mss_resid, 2),
                     round(anova(lmod)$'F value'[1], 2),
                     round(1 - ss_resid / ss_obsrv, 2),
                     round(summary(lmod)$r.squared, 2)))

print("Range of r squared from the individual models computed in the cv:")

summary(cv$model_r_squared)
```
*Question: why do i have in the command summary: Length  Class   Mode 
                                                  0   NULL   NULL?
When doing "leave-one out" I did get a result. I probably miscalculated something?                                                  

# The predictive model and its dataframe
```{r }
se <- function(x) sd(x, na.rm = TRUE)/sqrt(length(na.exclude(x)))

me <- round(mean(cv$pred - cv$obs, na.rm = TRUE), 2)
rmse <- round(sqrt(mean((cv$pred - cv$obs)^2, na.rm = TRUE)),2)
min_val <- round(min(cv$pred - cv$obs, na.rm = TRUE), 2)
quantile_25 <-round(quantile(cv$pred - cv$obs, c(0.25), type = 1))
quantile_50 <-round(quantile(cv$pred - cv$obs, c(0.5), type = 1))
quantile_75 <-round(quantile(cv$pred - cv$obs, c(0.75), type = 1))
max_val <- round(max(cv$pred - cv$obs, na.rm = TRUE),2)


data.frame (NAME = c("Mean error (ME)", "Root mean square error (RMSE)", 
                     "Minimum Value", "25% quantile", "50% quantile",
                     "75% quantile", "Maximum Value"),
            VALUE = c(me, rmse, min_val, 
                      quantile_25, quantile_50,
                      quantile_75, max_val))
```
#The predictive performance of the model: 
                           NAME  VALUE
1               Mean error (ME)  -0.02
2 Root mean square error (RMSE)   6.33
3                 Minimum Value -54.78
4                  25% quantile  -4.00
5                  50% quantile   0.00
6                  75% quantile   4.00
7                 Maximum Value  39.28