---
title: "da-ws-06-02"
author: "keltoskytoi, Jana Schönemann, Sebastian Richter"
date: "28 November 2016"
output: html_document
---
## I know that it has to be done with "leave many-out cross validation" but: wh does the "end dataframe" of the probability model differ so little? Did I miscalculte something? Or is it because "lmod" doesnt work in my R because obviously I don´t know which library to import (apart from car?)

```{r}
path_main <- "C:/Users/Keltoskytoi/Desktop/"
path_data <- paste0(path_main, "data/")
path_input <- paste0(path_data, "data_analysis/input/")
path_output <- paste0(path_data, "data_analysis/output/")
path_temp <- paste0(path_data, "data_analysis/temp/")
path_csv <- paste0(path_data, "data_analysis/csv/")
path_fun <- paste0(path_data, "data_analysis/fun/")

library(car)
library(lmtest)

```
# Organising the data
```{r}
df <- read.table(paste0(path_csv, "115-46-4_feldfruechte.txt"),
                 skip = 6, header = TRUE, sep = ";", dec = ",", fill = TRUE, 
                 encoding = "ANSI")

df <- df[1:8925,]

names(df) <-c("Year", "ID", "Place", "Winterweizen", "Roggen+Wintermenggetreide",  "Wintergerste",  "Sommergerste", "Hafer", "Triticale", "Kartoffeln", "Zuckerrüben", "Winterraps", "Silomais")

for (c in colnames(df) [4:13]){
  df[, c] [df[, c]== "."] <-NA
  df[, c] [df[, c]== "0,0"] <-NA
  df[, c] <- as.numeric(sub(",",".",as.character(df[, c])))
}

```
# Relation between Wintergerste and Winterweizen

```{r }
ind<-df$Wintergerste
dep<-df$Winterweizen
plot(dep, ind)
abline(lmod, col = "green")
```

# Preparations for the "leave one out cross validation" 

```{r }
nrow(df)
head(df)
df <- df[!is.na(df$Wintergerste), ]
df <- df[!is.na(df$Winterweizen), ]
remaining <- c("Wintergerste", "Winterweizen")
df_new <- df[, remaining]
head(df_new)
summary(df_new)
```
# Leave one out cross validation

```{r }
cv <- lapply(seq(nrow(df_new)), function(i){
  train <- df_new[-i, ]
  test <- df_new[i, ]
  lmod <- lm(Winterweizen ~ Wintergerste, data=train)
  pred <- predict(lmod , newdata = test)
  obsv <- test$Winterweizen
  data.frame(pred = pred,
             obsv = obsv,
             model_r_squared = summary(lmod)$r.squared)
})
cv <- do.call("rbind", cv)
summary(cv)
cv

ss_obsrv <- sum((cv$obsv - mean(cv$obsv))**2)
ss_model <- sum((cv$pred - mean(cv$obsv))**2)
ss_resid <- sum((cv$obsv - cv$pred)**2)

mss_obsrv <- ss_obsrv / (length(cv$obsv) - 1)
mss_model <- ss_model / 1
mss_resid <- ss_resid / (length(cv$obsv) - 2)

plot(cv$obsv, (cv$obsv - cv$pred))

```
# Organising the results in a dataframe

```{r }
data.frame(NAME = c("cross-validation F value",
                    "linear model F value", 
                    "cross-validatino r squared",
                    "linear model r squared"),
           VALUE = c(round(mss_model / mss_resid, 2),
                     round(anova(lmod)$'F value'[1], 2),
                     round(1 - ss_resid / ss_obsrv, 2),
                     round(summary(lmod)$r.squared, 2)))

print("Range of r squared from the individual models computed in the cv:")

summary(cv$model_r_squared)
```

# The predictive model
```{r }
se <- function(x) sd(x, na.rm = TRUE)/sqrt(length(na.exclude(x)))

me <- round(mean(cv$pred - cv$obs, na.rm = TRUE), 2)
rmse <- round(sqrt(mean((cv$pred - cv$obs)^2, na.rm = TRUE)),2)
min_val <- round(min(cv$pred - cv$obs, na.rm = TRUE), 2)
quantile_25 <-round(quantile(cv$pred - cv$obs, c(0.25), type = 1))
quantile_50 <-round(quantile(cv$pred - cv$obs, c(0.5), type = 1))
quantile_75 <-round(quantile(cv$pred - cv$obs, c(0.75), type = 1))
max_val <- round(max(cv$pred - cv$obs, na.rm = TRUE),2)
  

data.frame (NAME = c("Mean error (ME)", "Root mean square error (RMSE)", 
                    "Minimum Value", "25% quantile", "50% quantile",
                    "75% quantile", "Maximum Value"),
           VALUE = c(me, rmse, min_val, 
                     quantile_25, quantile_50,
                     quantile_75, max_val))
```
#The predictive performance of the model:
                           NAME  VALUE
1               Mean error (ME)   0.00
2 Root mean square error (RMSE)   6.33
3                 Minimum Value -54.52
4                  25% quantile  -4.00
5                  50% quantile   0.00
6                  75% quantile   4.00
7                 Maximum Value  39.21